Computer Science House By-Laws

### 2017-05-17 bylaws.tex

An Introductory Executive Board is elected by the introductory members to lead and manage the project as well as represent the introductory project participants to House.

@@

\bsubsubsection{Introductory Project Evaluations Process}
The Evaluations Director determines whether each introductory member passes or fails the Introductory Project by using information gathered from the Introductory Project Executive Board and the Introductory Project Advisors.
The Evaluations Director then reports the status of each Introductory Member's Introductory Project Evaluation to said Introductory Member.

@@

>>>>

An Introductory Executive Board is elected by the introductory members to lead and manage the project, represent the introductory project participants to House, and evaluate participants based on their contribution to the project.

@@

@@

At any point before the Introductory Evaluation, an Introductory Member may make a second attempt at the Introductory Packet by requesting a new Introductory Packet from the Evaluations Director.
Then, the Introductory Member goes through the \ref{Creation of Accounts} proccess once again. 
The best completion percentage of the two Introductory Packets will be presented at the Introductory Evaluation.
